\pagebreak
\nsection{Nuclei segmentation}

\begin{description}
    \item[\entry{Task:}] Measure the circularity, mean intensity and area of each nuclei in the image.
    \item[\entry{Data:}] The file “nuclei.tif” has a single channel “Mono”.
    \item[\entry{Topics:}] preprocessing (Rolling Ball, Median), segmentation (Threshold), measurement (Circularity, Mean Obj Intensity, Object Area)
    \item[\entry{Duration:}] 20 min
    \item[\entry{Step by step:}]
\end{description}

\begin{enumerate}
    \item Load the image “nuclei.tif” using “File > Open” or a drag and drop.
    \item Open the General analysis 3 interface using “Image > New GA3 recipe” or a right click on the background, select “Analysis Controls > Analysis Explorer”, select “Create New > General Analysis 3”. 
    \item Correct uneven background. \soln Use \menu{Preprocessing > Rolling Ball} with a radius equal to 26 px and tick \menu{Signal is bright}. \solnend \textcolor{olive}{Radius of the Rolling Ball should be larger than the object of interest.}
    \item Reduce the noise level. \soln For example, using a median filter with \menu{Preprocessing > Median}, set the radius to 2 px. \solnend
    \item Segment the nuclei. \soln Use \menu{Segmentation > Threshold > Threshold}. Set the with an intensity range in [12, 255], Smooth 1x, Clean 1x, FillHoles OFF, Separate 2x, Size[px] 10-max. \solnend
    \item Measure the circularity of the nuclei. \soln Use \menu{Measurement > Object shape > Circularity}. \solnend 
    \item Measure the mean intensity of the nuclei. \soln Use \menu{Measurement > Object intensity > Mean Obj Intensity} by setting the segmented region as the A (Binary) and the input as B (Color). \solnend
    \item Measure the area of the nuclei. \soln Use \menu{Measurement > Object size > Object Area}. \solnend
    \item To group the three records into one single record, press Ctrl and select the three modules the \menu{Circularity}, \menu{MeanObjIntensity} and \menu{ObjectArea} then right click and select “Make Group”.
    \item If needed do the same as in step 8 for RollingBall and Median modules.
\end{enumerate}

\begin{description}
    \item[\entry{Optional:}] scatter plot, find mitosis, etc
\end{description}
